Viscous Transport in Eroding Porous Media

### 2019-05-08 docs/transport/erosion_transport.tex
add new figs of the transport paper

\begin{figure}[H]
\begin{center}
\caption{The trajectories of tracers in the fluid with 20 bodies. The 6 snapshots are evenly spaced in time.}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
{\color{red}
The first nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b60}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b90}\\

\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b120}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b150}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b180}\\

\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b240}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270}
\caption{The trajectories of tracers in the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.}
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
{\color{red}
The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
